Coupling finite and boundary element methods to solve the Poisson-Boltzmann equation for electrostatics in molecular solvation

### 2022-03-29 results.tex
Update of results in the paper
added more refs

This section presents verification and performance results of the standard and hybrid FEM-BEM coupling schemes, for molecules modeled as cavities with constant and varying permittivity.
With a constant permittivity inside the molecule, we tested convergence against an analytical expression of the solvation energy of a sphere \cite{Kirkwood1934}, and then compared a more realistic geometry (arginine) with a purely BEM implementation.
We also considered a Gaussian-varying permittivity [Alexov and earlier] inside the molecular cavity of arginine, and used APBS \cite{BakerETal2001} to verify our results.
The final tests show the scaling of the standard and hybrid FEM-BEM coupling, as the molecule size grows.

@@

\begin{figure}
\centering
   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
   \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_error.png}
\caption{Solvation energy for arginine with a constant permittivity (left: Preconditioned systems, right: No preconditioner).
%maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?
}
\label{fig:arg_constant_energy}
\end{figure}

\begin{figure}
\centering
%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter.png}
  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time.png}
  \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_time.png}
\caption{Time-to-solution for arginine with a constant permittivity (left: Preconditioned systems, right: No preconditioner). NOTE: x axis differ between top and bottom. Also, should we include preconditioned vs non preconditioned? We could easily precondition BEM-BEM too.  %(1) fix title, (2) can we put them in a single plot, (3) 
%maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?
}
\label{fig:arg_constant_time}
\end{figure}

\begin{figure}
\centering
%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter.png}
  \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_iter.png}
%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time.png}
\caption{Iteration count for arginine with a constant permittivity (left: Preconditioned systems, right: No preconditioner). %(1) fix title, (2) can we put them in a single plot, (3) hybrid is internal or external iterations? maybe we should present the total count?
}
\label{fig:arg_contant_iter}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{c|c|c}
&Mesh size & $\Delta G_{solv}$\\
&\AA       &  kcal/mol \\
\hline
\multirow{4}{*}{APBS}& 0.52$\times$0.52$\times$0.52 & -32.4652\\ 
& 0.39$\times$0.39$\times$0.39 & -32.4042\\ 
&0.26$\times$0.26$\times$0.26 & -32.3375\\ 
&0.17$\times$0.17$\times$0.17 & -32.3413\\ 
\hline
&Mesh dens. & \\
&vert/\AA$^2$ & \\
\hline
%\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
    & 2 & -36.239\\
Standard    & 4  & -33.129 \\
FEM-BEM    & 8  & -32.674 \\
    & 16 & -32.293 \\
\hline
%\multirow{5}{*}{Standard FEM-BEM}& 2 & -29.554\\
    & 2 & -35.333\\
Hybrid    & 4  & -33.079 \\
FEM-BEM    & 8  & -32.660 \\
    & 16 & -32.359 \\
\hline
\end{tabular}
\caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using the standard and hybrid FEM-BEM approaches, and APBS. Add performance result?}
\label{table:arg_variable}
\end{table}

>>>>

This section presents verification and performance results of the standard and hybrid FEM-BEM coupling schemes, for molecules modeled as cavities with constant and varying permittivity.
With a constant permittivity inside the molecule, we tested convergence against an analytical expression of the solvation energy of a sphere \cite{Kirkwood1934}, and then compared a more realistic geometry (arginine) with a purely BEM implementation.
We also considered a Gaussian-varying permittivity\cite{grant2001smooth,li2013dielectric} inside the molecular cavity of arginine, and used APBS \cite{BakerETal2001} to verify our results.
The final tests show the scaling of the standard and hybrid FEM-BEM coupling, as the molecule size grows.

@@

\begin{figure}
\centering
   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
%    \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_error.png}
\caption{Solvation energy for arginine with a constant permittivity (left: Preconditioned systems, right: No preconditioner).
%maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?
}
\label{fig:arg_constant_energy}
\end{figure}

\begin{figure}
\centering
%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter.png}
  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time.png}
%   \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_time.png}
\caption{Time-to-solution for arginine with a constant permittivity (left: Preconditioned systems, right: No preconditioner). NOTE: x axis differ between top and bottom. Also, should we include preconditioned vs non preconditioned? We could easily precondition BEM-BEM too.  %(1) fix title, (2) can we put them in a single plot, (3) 
%maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?
}
\label{fig:arg_constant_time}
\end{figure}

\begin{figure}
\centering
%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter.png}
%   \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_iter.png}
%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time.png}
\caption{Iteration count for arginine with a constant permittivity (left: Preconditioned systems, right: No preconditioner). %(1) fix title, (2) can we put them in a single plot, (3) hybrid is internal or external iterations? maybe we should present the total count?
}
\label{fig:arg_contant_iter}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{c|c|c}
&Mesh size & $\Delta G_{solv}$\\
&\AA       &  kcal/mol \\
\hline
\multirow{4}{*}{APBS}& 0.52$\times$0.52$\times$0.52 & -32.4652\\ 
& 0.39$\times$0.39$\times$0.39 & -32.4042\\ 
&0.26$\times$0.26$\times$0.26 & -32.3375\\ 
&0.17$\times$0.17$\times$0.17 & -32.3413\\ 
\hline
&Mesh dens. & \\
&vert/\AA$^2$ & \\
\hline
%\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
    & 2 & -36.239\\
Standard    & 4  & -33.129 \\
FEM-BEM    & 8  & -32.673 \\
    & 16 & -32.293 \\
\hline
%\multirow{5}{*}{Standard FEM-BEM}& 2 & -29.554\\
    & 2 & -34.408\\
Hybrid    & 4  & -32.815 \\
FEM-BEM    & 8  & -32.566 \\
    & 16 & -32.379 \\
\hline
\end{tabular}
\caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using the standard and hybrid FEM-BEM approaches, and APBS. Add performance result?}
\label{table:arg_variable}
\end{table}
